%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Joshua Bas} % Your name
%\address{9111 Cedar River Road, Huntersville, NC 28078} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary address (optional)
\address{704.978.9370 \\ joshua.n.bas@gmail.com \\ Charlotte, NC} % Your phone number and email

\begin{document}

%-------------
%	EDUCATION
%-------------

\begin{Section}{Education}

{\bf Carnegie Mellon University}, Pittsburgh, PA \hfill {\em May 2020}
\\ B.S. in Electrical \& Computer Engineering\hfill %{ Overall Percentage: 68.14 }
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\

\end{Section}

%-----------------------
%	Relevant Coursework
%-----------------------
\begin{Section}{Relevant Coursework}

% \begin{tabular}{ @{} >{\series}l @{\hspace{6ex}} l }
\begin{tabular}{ll}

Logic Design \& Verification & Introduction to Computer Architecture \\
Introduction to Embedded Systems & Structure \& Design of Digital Systems \\
\end{tabular}

\end{Section}

%-------------------
%	WORK EXPERIENCE
%-------------------

\begin{Section}{Work Experience}

\begin{Subsection}{Audition Technology}{June 2019 - May 2020}{Analog Engineer Intern}{Pittsburgh, PA}
\item Researched digital hearing aid design and multiple hearing aid-specific DSP chips, including patents
\item Scouted an electrical device assembly facility as a potential manufacturing partner
\item Contributed to meetings with the startup's stakeholders and medical advisor
\item Proposed and designed a modular, 2-layer evaluation board
\item Created and maintained EagleCAD parts library
\end{Subsection}

\end{Section}

%-------------
%    Projects
%-------------
\begin{Section}{Projects}
\begin{Subsection}{RISCV Processor (SystemVerilog \& C)}{January 2020 - May 2020}{Introduction to Computer Architecture}
\item Designed and implemented a 6-stage dual-core processor for the RISCV ISA, particularly the RV32I base. Both cores are capable of the usual logical and arithmetical operations, as well as branches and unconditional jumps; the primary core can also access memory.
\end{Subsection}

\begin{Subsection}{Real-Time Kernel (C \& ARM Assembly)}{August 2019 - December 2019}{Introduction to Embedded Systems}
\item Implemented a simple real-time kernel on the STM32F microcontroller capable of executing SVCs and interrupt service routines; communicating via polled/interrupt UART, I2C, and SPI; receiving ADC inputs; and context swapping between different threads. Built on Ubuntu Linux.
\end{Subsection}

\begin{Subsection}{CMU Mars Ice (C/C++ \& Python)}{October 2018 - June 2019}{2019 Moon to Mars Ice \& Prospecting Challenge}
\item Created design blocks for PCB using EagleCAD for a drilling robot. Implemented a network with client dropped protocol, as well as the server-side controls system for the robot. Traveled to Langley Research Center to operate the robot.
\end{Subsection}

\begin{Subsection}{SDRAM Controller (SystemVerilog)}{October 2018 - June 2019}{Logic Design and Verification}
\item Designed a memory controller for a 64MB, 4-banked SDRAM, using VCS (Verilog Compiler Simulator) and Altera Quartus to debug and upload onto the Cyclone V FPGA.
\end{Subsection}

\end{Section}

\begin{Section}{Publications}
\item Development of Hearing Technology with Personalized Safe Listening Features. Gupta, S.; Xu, X.; Liu, H.; Zhang, J.; {\bf Bas, J.}; Kelly, S. 2019 ITU Kaleidoscope Conference Proceedings. 
\end{Section}

%------------------
%	Skills SECTION
%------------------

\begin{Section}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & C/C++, SystemVerilog, Python, ARM Assembly, MatLab\\%%, Java \\
Hardware \ & PCB design, circuit analysis, soldering\\
Software \& Tools \ & GDB, VCS, Valgrind, EagleCAD, Git, SolidWorks, MS Office\\
\end{tabular}

\end{Section}

%\newpage

%-----------------
% Extracurricular
%-----------------
% \begin{Section}{Extracurricular} \itemsep -3pt
% \item CMU Tartan Athletic Fellowship Leader (2017-2020)
% \item Community Service Trip | Pittsburgh, PA (Spring 2018)
% \item Community Service Trip | Webster Springs, WV (Spring 2017)
% \item Community Service Trip to Kusi Orphanage | Yungay, Peru (Spring 2016)

% \end{Section}

\end{document}
